Cluster Difference Imaging Photometric Survey. I. Light Curves of Stars in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-12 paper_I/ms.tex
update with (most) JH comments
Co-authored-by: joeldhartman <jhartman@astro.princeton.edu>

At the time of writing, two relatively large, homogeneous cluster
memberships studies had been performed using Gaia-DR2: those by
\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
There were also two large membership studies based on proper motion and 
photometric catalogs that were of interest: the studies of
\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}.

@@

To reduce the TESS images to light curves, we adopted a
difference imaging approach.  The overall method is in the spirit of the
pipelines developed by \citet{Pal_2009},
\citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017}, \citet{oelkers_precision_2018} and \citet{wallace_search_2019}.
Figure~\ref{fig:pipeline} shows a conceptual overview of
our pipeline.  Most modules have been
developed over the past decade to reduce
images taken by the Hungarian Automated Telescope (HAT) network \citep{bakos_hat_review_2018}.  The specific high-level framework
used for this reduction was adapted from a pipeline called
\texttt{pipe-trex}, under development primarily for the HATPI project
(\url{hatpi.org}).  The code is available
online\footnote{\url{github.com/waqasbhatti/pipe-trex}, commit
\texttt{cd9f9bb}.}.

We begin our processing with the calibrated full frame images produced
by the Science Processing Operations Center at NASA Ames
(\S~\ref{subsec:observations}).  We then perform a collection of
preparatory steps, including source extraction of bright stars,
astrometric verification, and coarse simple aperture photometry of
bright stars (\S~\ref{subsec:preparation}).  Using the information
collected from these initial steps, we select an astrometric reference
frame to which we transform all of the calibrated images. 
To construct a photometric reference frame,
we first convolve a subset of the frames to have identical stellar profiles,
and then stack them. Finally, we subtract each target frame
from the photometric reference frame (\S~\ref{subsec:imagesubtraction}).  We
perform aperture photometry on the subtracted images using positions
projected onto the frame from the Gaia-DR2 source catalog.  We detrend
the resulting light curves (\S~\ref{subsec:lcdetrending}).  The
resulting white noise and red noise properties of the light curves,
and a few interesting cases of variability, are discussed in
\S~\ref{sec:results}.

@@

First, we perform source extraction on the
thousand or so brightest, non-saturated stars in each image.  
This is done using a \texttt{fitsh} tool, \texttt{fistar}.
We derive centroid positions for the stars, and
simultaneously
fit elliptical gaussians to their profiles, yielding the shape
parameters $(s,d,k)$, where the flux $f$ as a function of position
$(x,y)$ in the CCD image plane is assumed to take the form
\begin{align}
  f(x,y) &= B + A \exp \{ -0.5 \times [
    s(\Delta x^2 + \Delta y^2) + \\
    \nonumber
    &d(\Delta x^2 - \Delta y^2) +
    k(2\Delta x \Delta y)
  ]  \},
\end{align}
for $(x_0,y_0)$ the central coordinates of the star,
$\Delta x = x-x_0$, $\Delta y = y - y_0$, $B$ the background
level, and $A$ an arbitrary
flux-scaling constant.
For a nearly circular shape profile, the sharpness $s$ is related to
the FWHM as ${\rm FWHM} \approx 2.35\sqrt{s}$ \citep[{\it
e.g.},][]{Pal_2009}.  These shape parameters are later used when
selecting an astrometric reference frame
(\S~\ref{subsec:imagesubtraction}).  
In agreement with what is obvious upon visual inspection, this 
fitting process shows that stars closer to the
center of each camera's field are round, while
stars near the field edges are more triangular.

@@

Figure~\ref{fig:astromresid} displays the residual between
the measured and projected stellar centroid
positions for one photometric reference image.
The plot shows that the errors
are typically largest in the corners of the image,
where the non-linearity of the focal plane is most significant, and
the corrections required by the SIP coefficients are largest.
Also, the typical median precision of the WCS solution is a bit below
0.1 pixels, and its $90^{\rm th}$ percentile is typically less than
0.3 pixels.
In our reduction,
we therefore require
that each frame's median residual and 90th percentile remain
below 0.2 and 0.4
pixels, respectively. If this constraint is not met, the reduction fails.
This is an essential quality-control check for any forced-aperture
photometry pipeline.
%The distribution has a outlier tail of saturated stars which were
%masked, and thus do not have measureable centroid positions.
%The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
%sanity check on the location of the projected positions, and also
%gives some context for our chosen aperture radii of 1, 1.5, and 2.25
%pixels.

@@

\subsubsection{History of image subtraction method}

@@

To choose the astrometric reference frame, we search for frames with
large, round stars (big $s$, small $d$ and $k$ values).  We also
require that the frame have a low background level, as measured in
annuli around the bright stars selected in
\S~\ref{subsec:preparation}.  Finally, the astrometric reference
frame needs to have a large
number of detected sources (though the variance between TESS images was rather 
small).  We sort the image
using these metrics, and then select the astrometric reference frame from
successive intersections of each sorted list.

@@

This kernel model has three free parameters: (1) the box-size; 
(2) the maximum order of the polynomial weighting the delta
function terms; (3) the maximum order of the polynomial weighting the
flux scaling.  We performed a grid-search to tune these parameters, in
which our ``loss functions'' were the light curve standard deviation (RMS)
as a function of magnitude, and the recovered SNR of transits from the catalog
of known TOIs (TESS Objects of Interest; N.~Guerrero, in prep).

@@

With a kernel selected, and the convolution and subtraction performed,
we calculate the instrumental fluxes for each frame per
Equation~\ref{eq:ism_flux_measurement}.  We did this with three
different aperture sizes: for this work, circles of radii 1 pixel, 1.5
pixels, and 2.25 pixels.  These sizes were chosen to roughly span the
range of optimal aperture sizes reported by
\citet{Sullivan_et_al_2015}.  Finally,
to convert from a list of flux measurements for each source on a frame
to a list of flux values at any given time, we used the
\texttt{fitsh} transposition tool \texttt{grcollect}.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.44\textwidth]{external_parameters_vs_time_sec6cam1ccd1.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    The variability in flux is sometimes correlated with variability
    in ``external'' parameters, shown here for a representative star
    over two orbits.  {\it Top}: Instrumental raw magnitude (with a
    particular aperture size), as a function of time.  Continuing in
    order are $x$ and $y$ centroid positions as a functions of time,
    the $(s,d,k)$ PSF shape parameters, the CCD temperature,  and the
    measured background value.  Differential aberration affect the
    centroid position over the span of each orbit.  Momentum dumps are
    marked with vertical dashed lines, and affect the measured shapes
    of stars.
		\label{fig:external_parameter_timeseries}
	}
\end{figure}

The preceding steps produce light curves that include both
instrumental systematics as well as astrophysical variability.
Figure~\ref{fig:lc_systematics_dtr} shows twenty stars of comparable
brightness randomly selected from two CCDs.  Stars that are far apart
on the same CCD often share similar changes in flux.  In other words,
the instrumental systematics seem to dominate.  This problem is
generic to most wide-field photometric datasets, including the WASP,
Kepler, and HAT surveys
\cite{Pollacco_2006,borucki_kepler_2010,bakos_hat_review_2018}.  To
remove the systematic variability, we adopted two different
approaches: {\it (i)} the trend-filtering algorithm (TFA,
\citealt{kovacs_trend_2005}), and {\it (ii)} a principal component
analysis (PCA).

@@

The idea of TFA is as follows.  Suppose we have $M$ ``template
stars'', which are a subsample of stars that represent all types of
systematics across the dataset.  Each template star has a light curve
with $N$ data points.  Denote the template time-series $X_j(i)$, where
$j={1,\ldots,M}$ and $i={1,\ldots,N}$ is the time index.  We then want
to find periodic signals in a target time-series $Y(i)$.  This is done
by defining a filter function
\begin{equation}
  F(i) = \sum_{j=1}^{M} c_j X_j(i),
\end{equation}
for which the coefficients $c_j$ are found by minimizing
\begin{equation}
  \mathcal{D} = \sum_{i=1}^{N} \left[ Y(i) - A(i) - F(i) \right]^2.
  \label{eq:tfa_to_minimize}
\end{equation}
When trying to find periodic signals, $A(i)$ represents our prior
knowledge of the light curve's shape.  This prior is simply that stars
on average maintain a constant brightness:
\begin{equation}
  A(i) = \langle Y \rangle = \frac{1}{N} \sum_{i=1}^{N} Y(i) = {\rm const.}
\end{equation}
If a signal is eventually found, for instance using the box-least
squares method \citep{kovacs_box-fitting_2002}, this detrending
process must then be repeated while accounting for our updated
knowledge about the light curve's shape.

Some implementation notes follow.  We selected template stars in two
stages.  In the first stage, we fitted a parabola in the RMS-magnitude
plane, and discarded stars more than $2\sigma$ away from the
prediction of the fit.  We also required that these initial candidate
stars have intermediate brightness ($8.5 > T > 13$), and have a
relatively large number of time-series data points.  We then performed
an initial iteration of TFA, on only the candidate template stars.  We
inspected the resulting detrended light curves for residual structure
by computing a Lomb-Scargle periodogram.  If the maximum-power peak
had a false alarm probability below 0.1\%, we excluded the star from
the list of candidate template stars, on the basis of its presumed
periodic variability.  We then randomly selected at most 200 template
stars from the remaining non-variable candidates.  The choice of
number of template stars was discussed by \citet{kovacs_trend_2005},
and is another free parameter in the broad problem of light curve
production.  This choice is analogous to the issue of how many
cotrending basis vectors to choose in PDC-MAP or ARC2
\citep{aigrain_robust_2017}.  While the number of template stars can
be optimized by constructing and minimizing a BIC-like quantity, a
little overfitting is acceptable for our pupose of finding planetary
transits.  For other applications, {\it e.g.,} stellar rotation period
searches, it is almost certainly preferable to adopt a less forceful
detrending approach.

@@

To remove the largest systematic trends with minimal overfitting of
{\it e.g.}, stellar rotation signals, we adopted a simple variant of
PCA (see {\it e.g.}, \citealt{ivezic_statistics_2014} for a review).
A similar approach was taken by \citet{feinstein_eleanor_2019} in
\texttt{eleanor}.  We derived the principal components for each CCD
using the 200 template stars previously selected for TFA.  We then
modelled each target light curve as a linear combination of a subset
of these principal components, with weights determined by linear least
squares.

To determine the ``optimal'' number of principal components to use, we
performed a cross-validation analysis on the template stars using the
components derived both from PCA, as well as a separate factor
analysis.  As is typically the case when the noise variance is
different for each ``feature'' (each point in time), we found that
$k$-folding cross-validation using PCA failed to recover a plausible
number of components\footnote{See for example
\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}
 (2019/08/06).}.
However, the factor analysis typically maximized the cross-validation
score with anywhere from $10$ to $15$ components, which agreed with a
visual analysis of the number of PCA components past which overfitting
began.  We therefore used the maximum cross-validation score from
thefactor analysis as the number of principal components to use in
each light curve.  This number is documented in the \texttt{FITS}
header of each light curve.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{quilt_s6_s7.pdf}
	\end{center}
	\vspace{-0.8cm}
	\caption{
		Phased light curves for a few objects of interest.
		{\it Top row, left to right}:
		TOI~496 in Messier 48;
		TOI~625 orbiting a late A dwarf;
		and an eccentric EB in Bochum~5.
		{\it Middle row, left to right}:
		A detached EB in a 80~Myr old cluster;
		V684 Mon (a 10 Myr old detached EB);
		and a semi-detached EB in NGC 2548.
		{\it Bottom row, left to right}:
		Spotted rotator in NGC 2184;
		a pulsator or perhaps EB flagged by \citet{zari_3d_2018} as a pre-MS 
		star;
		and a quasi-periodic pulsator, also with a pre-MS host.
		Gaia source identifiers are given in the text.
	\label{fig:quilt}
	}
\end{figure*}

@@

\paragraph{Sector 6}
In Sector 6, \sVInumberlcs light curves of candidate cluster stars
were made. The provenance of the target star for these
sources is \citet{dias_proper_2014} for 40\% of the sources;
\citet{zari_3d_2018} for 11\% of sources from their upper
main-sequence table and 7\% of sources from their PMS table;
\citet{Kharchenko_et_al_2013} for 18\% of sources,
\citet{cantat-gaudin_gaia_2018} for 14\% of sources, and more than two
catalogs for the remaining 10\% of sources.

@@

Beyond the white noise properties of the light curves, the red noise
properties are also important. 
In Figure~\ref{fig:avg_acf} we show the average autocorrelation of the
raw, PCA, and TFA light curves.
The raw light curves have substantial red noise, and
their average autocorrelation across many time lags is
positive.
The PCA and TFA light curves are much closer to gaussian~--~the
average autocorrelation between any two points in these light curves
is close to zero.
However, the average PCA and TFA light curves are not {\it exactly}
gaussian.
At time lags of a few hours or less, there is some excess power.
This suggests that additional detrending may be
necessary to maximize the effectiveness of planet searches, or the discovery of
any other signals via matched-filter techniques.

@@

The overall point is that a great number of systems with known ages
should be identifiable from the data at their current level of
preparation.

@@

The light curves seem to be limited in precision by photon-counting noise 
from the target star at
the bright end, and by unresolved background stars at the faint end
(Figure~\ref{fig:rms_vs_mag}).
Though the raw light curves show significant red noise, decorrelating
against a set of template stars led to an ensemble of light curves
with very nearly gaussian noise properties 
(Figures~\ref{fig:lc_systematics_dtr} and~\ref{fig:avg_acf}).

@@

Despite our goal of completeness, some clusters may still be missing
members~--~the census of nearby coeval stellar populations is still
very much in flux. For instance, in the preparation of this work,
\citet{sim_open_2019} identified 209 new open cluster candidates
within 1~kpc through visual inspection of Gaia-DR2 data.  Similarly,
\citet{kounkel_untangling_2019} searched for groups near
the galactic plane within 1~kpc, and along with the known clusters
found hundreds of new ``strings'' of kinematically associated stars, which
could be coeval.

@@

    \tablecomments{
    This table is published in its entirety in a 
    machine-readable format.
    A portion of the transposed version
    is shown here for guidance regarding its form and content.
    Each row in the machine-readable version (each column in this
    version) represents a target star.
    The unique identifier, ``ID'', is the Gaia-DR2 source identifier.
    The external catalog(s) claiming cluster membership is given 
    as a comma-separated string in
    ``Reference'', and the name they assign is given as a comma-separated
    string in ``Cluster''.
    ``Ext catalog name'' is the name the external catalog assigns.
    Positions, proper motions, and the parallax are from Gaia-DR2.
    The magnitudes in Gaia $G$, $G_{\rm Bp}$, and $G_{\rm Rp}$ bands
    is given.
    The naming matching described in Appendix~\ref{appendix:uniquenames}
    most often succeeds in finding the
    \citet{Kharchenko_et_al_2013} (K13) cluster corresponding to
    the external catalog claiming membership.
    This, or else the external name is used to assign the unique
    cluster name.
    The method for name matching (Appendix~\ref{appendix:uniquenames}) is
    also given as a string, as is a ``Comment'' summarizing
    information from \citet{Kharchenko_et_al_2013} about the
    cluster.
    The age and error as quoted by \citet{Kharchenko_et_al_2013}
    are also given.
}

@@

\begin{deluxetable}{lll}
	\tablecaption{Counts of light curves per cluster in Sector 7, sorted
		in descending order.  \label{tbl:s7_lcs}}
	\tablenum{3}

@@

The time-stamps included with the calibrated TESS Full Frame Images
produced by SPOC include a barycenteric correction at
a single reference pixel given at the middle of every frame.
The barycentric correction is at maximum 16 minutes, corresponding to
points on the sky separated by 180 degrees.
The angular distance from a TESS camera's center of field to the corners
is $\approx$17 degrees, so naively one might incur at worst an error of
$\approx$90 seconds on the time-stamps due to using a barycentric
correction in a direction that is slightly wrong.
Perhaps due to the lead author's obsession with getting time-stamps correct 
\citep{bouma_wasp-4b_2019},
we perform our own barycentric correction using the appropriate
sky coordinates for each light curve.
We advise use of our \texttt{TMID\_BJD} column, which gives the
mid-time of each exposure in the BJD$_{\rm TDB}$ time system, which
is the defacto standard in exoplanet and stellar
astronomy~\citep{eastman_achieving_2010}.

@@

A few edge-cases, including for instance sub-clusters  larger
star-forming complexes like in Sco-Cen or Collinder~33, were 
manually resolved to the extent feasible (\citealt{rizzuto_multidimensional_2011}
and \citealt{saurin_isolating_2015} give
detailed pictures of the complex morphologies that frequently arise in
young star-forming regions).

>>>>

At the time of writing, two relatively large, homogeneous cluster
memberships studies had been performed using Gaia-DR2: those by
\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
There were also two large membership studies pre-dating Gaia-DR2 based on proper motion and 
photometric catalogs: the studies of
\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}.

@@

To reduce the TESS images to light curves, we adopted a
difference imaging approach.  The overall method is in the spirit of the
pipelines developed by \citet{Pal_2009},
\citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017}, \citet{oelkers_precision_2018} and \citet{wallace_search_2019}.
Figure~\ref{fig:pipeline} shows a conceptual overview of
our pipeline.  Most modules have been
developed over the past decade to reduce
images taken by the Hungarian Automated Telescope (HAT) network \citep{bakos_hat_review_2018}.
The work of \citet{Pal_2009}, embodied in the \texttt{fitsh} software package,
was an especially crucial component.
The specific high-level framework
we used for this reduction was adapted from a pipeline called
\texttt{pipe-trex}, under development primarily for the HATPI project
(\url{hatpi.org}).  The code is available
online\footnote{\url{github.com/waqasbhatti/pipe-trex}, commit
\texttt{cd9f9bb}.}.

We begin our processing with the calibrated full frame images produced
by the Science Processing Operations Center at NASA Ames
(\S~\ref{subsec:observations}).  We then perform a collection of
preparatory steps, including source extraction of bright stars,
astrometric verification, and coarse simple aperture photometry of
bright stars (\S~\ref{subsec:preparation}).  Using the information
collected from these initial steps, we select an astrometric reference
frame to which we transform all of the calibrated images. 
To construct a photometric reference frame,
we first convolve a subset of the frames to have identical stellar profiles,
and then stack them. Finally, we subtract each target frame
from the photometric reference frame (\S~\ref{subsec:imagesubtraction}).  We
perform aperture photometry on the subtracted images using positions
projected onto the frame from the Gaia-DR2 source catalog.  
The resulting differential flux measurements are converted to total flux measurements using photometric information from Gaia-DR2 to estimate the total flux of each source on the reference image.
We detrend
the resulting light curves (\S~\ref{subsec:lcdetrending}).  The
resulting white noise and red noise properties of the light curves,
and a few interesting cases of variability, are discussed in
\S~\ref{sec:results}.

@@

First, we perform source extraction on the
thousand or so brightest, non-saturated stars in each image.  
This is done using a \texttt{fitsh} tool, \texttt{fistar}.
We derive centroid positions for the stars, and
simultaneously
fit elliptical gaussians to their profiles, yielding the shape
parameters $(s,d,k)$, where the flux $f$ as a function of position
$(x,y)$ in the CCD image plane is assumed to take the form
\begin{align}
  f(x,y) &= B + A \exp \{ -0.5 \times [
    s(\Delta x^2 + \Delta y^2) + \\
    \nonumber
    &d(\Delta x^2 - \Delta y^2) +
    k(2\Delta x \Delta y)
  ]  \},
\end{align}
for $(x_0,y_0)$ the central coordinates of the star,
$\Delta x = x-x_0$, $\Delta y = y - y_0$, $B$ the background
level, and $A$ an arbitrary
flux-scaling constant.
For a nearly circular shape profile, the sharpness $s$ is related to
the FWHM as ${\rm FWHM} \approx 2.35s^{-1/2}$ \citep[{\it
e.g.},][]{Pal_2009}.  These shape parameters are later used when
selecting an astrometric reference frame
(\S~\ref{subsec:imagesubtraction}).  
In agreement with what is obvious upon visual inspection, this 
fitting process shows that stars closer to the
center of each camera's field are round, while
stars near the field edges are more elongated.

@@

Figure~\ref{fig:astromresid} displays the residual between
the measured and projected stellar centroid
positions for one photometric reference frame.
The construction of this frame will be described shortly.
The plot shows that the errors
are typically largest in the corners of the image,
where the non-linearity of the focal plane is most significant, and
the corrections required by the SIP coefficients are largest.
Also, the typical median precision of the WCS solution is a bit below
0.1 pixels, and its $90^{\rm th}$ percentile is typically less than
0.3 pixels.
In our reduction,
we therefore require
that each frame's median residual and 90th percentile remain
below 0.2 and 0.4
pixels, respectively. If this constraint is not met, the reduction fails.
This is an essential quality-control check for any forced-aperture
photometry pipeline.
%The distribution has a outlier tail of saturated stars which were
%masked, and thus do not have measureable centroid positions.
%The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
%sanity check on the location of the projected positions, and also
%gives some context for our chosen aperture radii of 1, 1.5, and 2.25
%pixels.

@@

\subsubsection{Synopsis of image subtraction method}

@@

To choose the astrometric reference frame, we search for frames with
compact, round stars (big $s$, small $d$ and $k$ values).  We also
require that the frame have a low background level, as measured in
annuli around the bright stars selected in
\S~\ref{subsec:preparation}.  Finally, the astrometric reference
frame needs to have a large
number of detected sources (though the variance between TESS images was rather 
small).  We sort the image
using these metrics, and then select the astrometric reference frame from
successive intersections of each sorted list.

@@

This kernel model has three parameters that must be
specified, but are not automatically optimized by the procedure: (1) the box-size; 
(2) the maximum order of the polynomial weighting the delta
function terms; (3) the maximum order of the polynomial weighting the
flux scaling.  We performed a grid-search to tune these parameters, in
which our ``loss functions'' were the light curve standard deviation (RMS)
as a function of magnitude, and the recovered SNR of transits from the catalog
of known TOIs (TESS Objects of Interest; N.~Guerrero, in prep).

@@

With a kernel selected, and the convolution and subtraction performed,
we calculate the instrumental fluxes for each frame per
Equation~\ref{eq:ism_flux_measurement}.  We did this with three
different aperture sizes: for this work, circles of radii 1 pixel, 1.5
pixels, and 2.25 pixels.  These sizes were chosen to roughly span the
range of optimal aperture sizes reported by
\citet{Sullivan_et_al_2015}.  Finally,
to convert from a list of flux measurements for each source on a frame
to light curves, we used the
\texttt{fitsh} transposition tool \texttt{grcollect}.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{external_parameters_vs_time_sec6cam1ccd1.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    The variability in flux is sometimes correlated with variability
    in ``external'' parameters, shown here for a representative star
    over two orbits.  {\it Top}: Instrumental raw magnitude (with a
    particular aperture size), as a function of time.  Continuing in
    order are $x$ and $y$ centroid positions as functions of time,
    the $(s,d,k)$ PSF shape parameters, the CCD temperature,  and the
    measured background value.  Differential aberration affects the
    centroid position over the span of each orbit.  Momentum dumps are
    marked with vertical dashed lines, and affect the measured shapes
    of stars.
		\label{fig:external_parameter_timeseries}
	}
\end{figure}

The preceding steps produce light curves that include both
instrumental systematics as well as astrophysical variability.
Figure~\ref{fig:lc_systematics_dtr} shows twenty stars of comparable
brightness randomly selected from two CCDs.  Stars that are far apart
on the same CCD often share similar changes in flux.  In other words,
the instrumental systematics seem to dominate.  This problem is
generic in wide-field photometric datasets, including the WASP,
Kepler, and HAT surveys
\citep{Pollacco_2006,borucki_kepler_2010,bakos_hat_review_2018}.  To
remove the systematic variability, we adopted two different
approaches: {\it (i)} the trend-filtering algorithm (TFA,
\citealt{kovacs_trend_2005}), and {\it (ii)} a principal component
analysis (PCA, see {\it e.g.}, \citealt{ivezic_statistics_2014} for a review).

@@

The idea of TFA is as follows.  Suppose we have $M$ ``template
stars'', which are a subsample of stars that represent all types of
systematics across the dataset.  Each template star has a light curve
with $N$ data points.  Denote the template time-series $X_j(i)$, where
$j={1,\ldots,M}$ and $i={1,\ldots,N}$ is the time index.  We then want
to find periodic signals in a target time-series $Y(i)$.  This is done
by defining a filter function
\begin{equation}
  F(i) = \sum_{j=1}^{M} c_j X_j(i),
\end{equation}
for which the coefficients $c_j$ are found by minimizing
\begin{equation}
  \mathcal{D} = \sum_{i=1}^{N} \left[ Y(i) - A(i) - F(i) \right]^2.
  \label{eq:tfa_to_minimize}
\end{equation}
When trying to find periodic signals, $A(i)$ represents our prior
knowledge of the light curve's shape.  Initially, this prior is simply that stars
on average maintain a constant brightness:
\begin{equation}
  A(i) = \langle Y \rangle = \frac{1}{N} \sum_{i=1}^{N} Y(i) = {\rm const.}
\end{equation}
If a signal is eventually found, for instance using the box-least
squares method \citep{kovacs_box-fitting_2002}, this detrending
process must then be repeated while accounting for our updated
knowledge about the light curve's shape.

Some implementation notes follow.  We selected template stars in two
stages.  In the first stage, we fitted a parabola in the RMS-magnitude
plane, and discarded stars more than $2\sigma$ away from the
prediction of the fit.  We also required that these initial candidate
stars have intermediate brightness ($8.5 > T > 13$), and have a
relatively large number of time-series data points.  
We excluded templates within 20 pixels of any given target star.
We then performed
an initial iteration of TFA, on only the candidate template stars.  We
inspected the resulting detrended light curves for residual structure
by computing a Lomb-Scargle periodogram.  If the maximum-power peak
had a false alarm probability below 0.1\%, we excluded the star from
the list of candidate template stars, on the basis of its presumed
periodic variability.  We then randomly selected at most 200 template
stars from the remaining non-variable candidates.  The choice of
number of template stars was discussed by \citet{kovacs_trend_2005},
and is another free parameter in the broad problem of light curve
production.  This choice is analogous to the issue of how many
cotrending basis vectors to choose in PDC-MAP or ARC2
\citep{aigrain_robust_2017}.  While the number of template stars can
be optimized by constructing and minimizing a BIC-like quantity, a
little overfitting is acceptable for our pupose of finding planetary
transits.  For other applications, {\it e.g.,} stellar rotation period
searches, it is almost certainly preferable to adopt a less forceful
detrending approach.

@@

To remove the largest systematic trends with minimal overfitting of
{\it e.g.}, stellar rotation signals, we adopted a simple variant of
PCA.
A similar approach was taken by \citet{feinstein_eleanor_2019} in
\texttt{eleanor}.  We derived the principal components for each CCD
using the 200 template stars previously selected for TFA.  We then
modelled each target light curve as a linear combination of a subset
of these principal components, and determined the weights via linear least
squares. Both steps were performed using \texttt{scikit-learn}
\citep{sklearn_2011}.

To determine the number of principal components at which to truncate
the model, we
performed a cross-validation analysis.
Again, this was achieved using \texttt{scikit-learn}.
As is typically the case when the noise variance is
different for each ``feature'' (each point in time), we found that
$k$-folding cross-validation of the PCA components
gave a cross-validation score that monotonically increased with
an increasing 
number of components\footnote{See for example
\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}
 (2019/08/06).}.
We found that if we instead performed a factor analysis, the
cross-validation
score was typically maximized with anywhere from $10$ to $15$ components.
This agreed with a
visual analysis of the number of PCA components past which overfitting
began.  We therefore used the maximum cross-validation score from
the factor analysis as the number of principal components to use in
each light curve.  This number is documented in the \texttt{FITS}
header of each light curve.

While the PCA detrending should help remove the most egregious
systematic artifacts, it remains possible that PCA can distort signals,
and even inject correlated noise into a light curve ({\it e.g.}, Figure~\ref{fig:lc_systematics_dtr}).
For any object of interest, it is worth inspecting the raw, PCA, and TFA
light curves to ensure
that the variability of interest is not adversely affected by the
detrending procedures.
If it is, alternative approaches may be necessary.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{quilt_s6_s7.pdf}
	\end{center}
	\vspace{-0.8cm}
	\caption{
		Phased PCA light curves for a few objects of interest.
		{\it Top row, left to right}:
		TOI~496 in Messier 48;
		TOI~625 orbiting a late A dwarf;
		and an eccentric EB in Bochum~5.
		{\it Middle row, left to right}:
		A detached EB in a 80~Myr old cluster;
		V684 Mon (a 10 Myr old detached EB);
		and a semi-detached EB in NGC 2548.
		{\it Bottom row, left to right}:
		Spotted rotator in NGC 2184;
		a pulsator or perhaps EB flagged by \citet{zari_3d_2018} as a pre-MS 
		star;
		and a quasi-periodic pulsator, also with a pre-MS host.
		Gaia source identifiers are given in the text.
	\label{fig:quilt}
	}
\end{figure*}

@@

\paragraph{Sector 6}
In Sector 6, \sVInumberlcs light curves of candidate cluster stars
were made. The provenance of the target star for these
sources is \citet{dias_proper_2014} for 40\% of the sources;
\citet{zari_3d_2018} for 11\% of sources from their upper
main-sequence table and 7\% of sources from their PMS table;
\citet{Kharchenko_et_al_2013} for 18\% of sources;
\citet{cantat-gaudin_gaia_2018} for 14\% of sources; and more than two
catalogs for the remaining 10\% of sources.

@@

Beyond the white noise properties of the light curves, the red noise
properties are also important. 
In Figure~\ref{fig:avg_acf} we show the average autocorrelation of the
raw, PCA, and TFA light curves.
The raw light curves have substantial red noise, and
their average autocorrelation across many time lags is
positive.
The PCA and TFA light curves are much closer to white noise~--~the
average autocorrelation between any two points in these light curves
is close to zero.
However, the average PCA and TFA light curves are not {\it completely}
uncorrelated.
At time lags of a few hours or less, there is some excess power.
This suggests that additional detrending may be
necessary to maximize the effectiveness of planet searches, or the discovery of
any other signals via matched-filter techniques.

@@

Overall, our periodogram search showed that 7\% of the light curves
have Lomb-Scargle peak false alarm probabilities below $10^{-30}$.
Even more stars are variable at lower levels of signifiance.
The implication is that thousands of variable stars with known ages
should be identifiable from the data at their current level of
preparation.

@@

The light curves seem to be limited in precision by photon-counting noise 
from the target star at
the bright end, and by unresolved background stars at the faint end
(Figure~\ref{fig:rms_vs_mag}).
Though the raw light curves show significant red noise, decorrelating
against a set of template stars led to an ensemble of light curves
with very nearly white noise properties 
(Figures~\ref{fig:lc_systematics_dtr} and~\ref{fig:avg_acf}).

@@

Despite our goal of completeness, some clusters may still be missing
members~--~the census of nearby coeval stellar populations is still
very much in flux. For instance, during the preparation of this work,
\citet{sim_open_2019} identified 209 new open cluster candidates
within 1~kpc through visual inspection of Gaia-DR2 data.  Similarly,
\citet{kounkel_untangling_2019} searched for groups near
the galactic plane within 1~kpc, and along with the known clusters
found hundreds of new ``strings'' of kinematically associated stars, which
could be coeval.

@@

    \tablecomments{
    This table is published in its entirety in a 
    machine-readable format.
    A portion of the transposed version
    is shown here for guidance regarding its form and content.
    Each row in the machine-readable version (each column in this
    version) represents a target star.
    The unique identifier, ``ID'', is the Gaia-DR2 source identifier.
    The external catalog(s) claiming cluster membership is given 
    as a comma-separated string in
    ``Reference'', and the name they assign is given as a comma-separated
    string in ``Cluster''.
    ``Ext catalog name'' is the name the external catalog assigns.
    Positions, proper motions, and the parallax are from Gaia-DR2.
    The magnitudes in Gaia $G$, $G_{\rm Bp}$, and $G_{\rm Rp}$ bands
    are given.
    The name matching described in Appendix~\ref{appendix:uniquenames}
    most often succeeds in finding the
    \citet{Kharchenko_et_al_2013} (K13) cluster corresponding to
    the external catalog claiming membership.
    This, or else the external name is used to assign the unique
    cluster name.
    The method for name matching (Appendix~\ref{appendix:uniquenames}) is
    also given as a string, as is a ``Comment'' summarizing
    information from \citet{Kharchenko_et_al_2013} about the
    cluster.
    The age and error as quoted by \citet{Kharchenko_et_al_2013}
    are also given.
}

@@

\begin{deluxetable}{lll}
	\tablecaption{Counts of light curves per cluster in Sector 7, sorted
		in descending order.  See Table~\ref{tbl:s6_lcs} for notes. \label{tbl:s7_lcs}}
	\tablenum{3}

@@

The time-stamps included with the calibrated TESS Full Frame Images
produced by SPOC include a barycenteric correction at
a single reference pixel given at the middle of every frame.
The barycentric correction is at maximum 16 minutes, corresponding to
points on the sky separated by 180 degrees.
The angular distance from a TESS camera's center of field to the corners
is $\approx$17 degrees, so naively one might incur at worst an error of
$\approx$90 seconds on the time-stamps due to using a barycentric
correction in a direction that is slightly wrong.
Nonetheless, following
\citet{bouma_wasp-4b_2019},
we perform our own barycentric correction using the appropriate
sky coordinates for each light curve.
We advise use of our \texttt{TMID\_BJD} column, which gives the
mid-time of each exposure in the BJD$_{\rm TDB}$ time system, which
is the defacto standard in exoplanet and stellar
astronomy~\citep{eastman_achieving_2010}.

@@

A few edge-cases, including sub-clusters of larger
star-forming complexes like in Sco-Cen or Collinder~33, were 
manually resolved to the extent feasible (\citealt{rizzuto_multidimensional_2011}
and \citealt{saurin_isolating_2015} give
detailed pictures of the complex morphologies that frequently arise in
young star-forming regions).
